---
title:           Find Doctor Shopping
author:          Dennis Wollersheim and Stephen Callinan
date:            11.07.2018
linkcolor:       cyan
citecolor:       grey
output:
pdf_document:
  highlight:   zenburn
---

\tableofcontents

# motivation 

Get all 

```{r results='hide', message=FALSE, warning=FALSE}

data_source_suffix='_rr'
data_source_suffix=''

intersect_filename = paste0( 'data/df_intersect', data_source_suffix, '.rda')

source('lib/functions.R')
source( "lib/get_data.R")
# -------------------------------------------------



my_db_get_query ( paste0( " 
      select pin, spply_dt, pbs_code, pbs_rgltn24_adjst_qty as quantity
      from pbs", data_source_suffix, " 
      JOIN pbs_item pi USING (pbs_code) 
      WHERE pi.atc_code LIKE 'N02A%' ")) %>%
  as.tibble() %>% 
  { . } -> df_pbs

my_db_get_query ( paste0( " select * from patient", data_source_suffix)) %>%
  as.tibble() %>% 
  mutate( age = 2004 - yob , 
         age_group=cut( age, breaks=0:6*20 )) %>%
  { . } -> df_people


my_db_get_query ( paste0( " 
            select pin, date_of_service as spply_dt, spr, spr_rsp, rpr
            from mbs", data_source_suffix, 
            " where item in (
                    select item
                    from mbs_rr JOIN mbs_desc_latest USING (item)
                    where description like '%attendance%'
                    group by 1
                    order by count(*) desc
                    limit 20
            ) AND
            pin in (
            select pin
            from pbs", data_source_suffix, " 
            JOIN pbs_item pi USING (pbs_code) 
            WHERE pi.atc_code LIKE 'N02A%') 
  ")) %>%
  as.tibble() %>% 
  { . } -> df_mbs

```

# Analyse data 

  - for each patient
  - for each script, calculate start and end

```{r}

find_multi_script_group <- function  (supply_date, ndays ) {
  overlap = 1
  pos = 1
  group_id = 0
  rv=c()
  while (pos <= length( ndays )) {
    start_group = pos
    end_date = supply_date[ pos ] + ndays[ pos ] + overlap

    pos = pos + 1
    in_session=TRUE
    while ( (pos <= length( ndays )) &
           (supply_date[pos] - overlap < end_date) 
         ) {
      end_date = supply_date[ pos ] + ndays[ pos ] + overlap
      pos = pos + 1
    }
    rv = c(rv, rep( group_id, pos - start_group  ))
    group_id = group_id + 1
  }
  rv
}


```

 1) find contiguious and/or overlapping multi drug episodes
 2) find the doctor consults within that period
 3) create df_intersect, containing every intersection of the entire multi script episode with any doctor consults

```{r}




if (file.exists( intersect_filename )) {
  load( intersect_filename, verbose=TRUE )
} else {
  #


  df_pbs %>%
    mutate( row_id = row_number() ) %>%
    group_by( pin ) %>%
    arrange( pin, spply_dt ) %>%
    mutate( group = find_multi_script_group( spply_dt, quantity)) %>%
    group_by( pin, group ) %>%
    arrange( pin, spply_dt, group ) %>% 
    mutate( gl = max( spply_dt ) - min(spply_dt ), 
           ndays = sum(quantity ),
           nscripts = n()) %>%
    filter( nscripts > 1 ) %>% 
    { . } -> df_pbs_multi_groups
  #
  #
  df_pbs_multi_groups  %>%
    group_by( pin, group, nscripts ) %>%
    summarise( start_date = min( spply_dt ) - 7, 
              end_date = max( spply_dt ),
              quantity = sum(quantity)
              ) %>%
    group_by( pin ) %>%
    select( pin,  start_date, end_date, group, quantity, nscripts) %>% 
    nest( start_date, end_date,  group, quantity, nscripts, .key=pbs ) %>%
    { . } -> df_pbs_nested
  #
  #
  df_mbs %>%
    group_by(pin) %>%
    mutate( end_date = spply_dt + 7,
           start_date = spply_dt - 7) %>%
     select( pin, spr, spply_dt, start_date, end_date) %>% 
    nest( spr, spply_dt, start_date, end_date, .key=mbs ) %>%
    { . } -> df_mbs_nested
  #
  #
  no_cores <- detectCores() - 1
  cluster <- create_cluster(no_cores)
  #
  df_mbs_nested %>%
    inner_join( df_pbs_nested ) %>% 
    partition(pin, cluster=cluster )  %>%
    { . } -> df_both
  #
  cluster_library(df_both, c("tidyverse", "IRanges", "fuzzyjoin"))
  #
  #
  df_both %>%
    do( joined = interval_inner_join( data.frame(.$mbs), 
                                     data.frame(.$pbs), 
                                     by=c('start_date','end_date') ))  %>%
  collect() %>%
  ungroup() %>%
  unnest() %>% 
  { . } -> df_intersect
  #
  #
  #
  save(df_intersect, file=intersect_filename)

}

```

# analysis - number of distinct practicioners for each period the period

```{r analysis1}

df_intersect %>%
  group_by( pin, spr ) %>%
  summarise( pills = sum( n ), nsegments = n() ) %>%
  ungroup() %>%
  arrange( desc( mn ))


```

# analysis - number of distinct practicioners over the period

```{r analysis2}

df_intersect %>%
  mutate( ndays = end_date.y - start_date.y ) %>%
  filter( ndays < 2000 ) %>%
  group_by( pin, group, ndays ) %>%
  distinct( spr ) %>%
  count() %>%
  mutate( days_per_spr = ndays / n ) %>%
  arrange( desc( n )) %>%
  ggplot( aes( n, days_per_spr, color= log(as.numeric( ndays ) )) ) + 
  geom_point() +
  xlab( "Number of distinct SPR" ) +
  ylab( "Days per distinct SPR" ) 


```

# analysis - number of distinct practicioners over the period

```{r analysis3}


```

# analysis - number of distinct practicioners over the period

```{r analysis4}

```
