---
title:           Find Doctor Shopping
author:          Dennis Wollersheim and Stephen Callinan
date:            11.07.2018
linkcolor:       cyan
citecolor:       grey
output:
pdf_document:
  highlight:   zenburn
---

\tableofcontents


Try to find the doctor shoppers from within the pbs

## algorithm
  - find overlapping scripts
  - find multiple prescribers within 2 weeks of overlap


```{r results='hide', message=FALSE, warning=FALSE}

data_source_suffix=''
data_source_suffix='_rr'
data_source_suffix='_r'

intersect_filename = paste0( 'data/df_intersect', data_source_suffix, '.rda')

source('lib/functions.R')
source( "lib/get_data.R")
# -------------------------------------------------



my_db_get_query ( paste0( " 
      select pin, spply_dt, pbs_code, pbs_rgltn24_adjst_qty as quantity
      from pbs", data_source_suffix, " 
      JOIN pbs_item pi USING (pbs_code) 
      WHERE pi.atc_code LIKE 'N02A%' ")) %>%
  as.tibble() %>% 
  { . } -> df_pbs

my_db_get_query ( paste0( " select * from patient", data_source_suffix)) %>%
  as.tibble() %>% 
  mutate( age = 2004 - yob , 
         age_group=cut( age, breaks=0:12*10 )) %>%
  { . } -> df_people


my_db_get_query ( paste0( " 
            select pin, date_of_service as spply_dt, spr, spr_rsp, rpr
            from mbs", data_source_suffix, 
            " where item in ( '00023', '00005', '00053'
            ) AND
            pin in (
            select pin
            from pbs", data_source_suffix, " 
            JOIN pbs_item pi USING (pbs_code) 
            WHERE pi.atc_code LIKE 'N02A%') 
  ")) %>%
  as.tibble() %>% 
  { . } -> df_mbs

```

# Analyse data 

  - for each patient
  - for each script, calculate start and end

```{r}

find_multi_script_group <- function  (supply_date, ndays ) {
  overlap = 5
  pos = 1
  group_id = 0
  rv=c()
  while (pos <= length( ndays )) {
    start_group = pos
    end_date = supply_date[ pos ] + ndays[ pos ] + overlap

    pos = pos + 1
    in_session=TRUE
    while ( (pos <= length( ndays )) &
           (supply_date[pos] - overlap < end_date) 
         ) {
      end_date = supply_date[ pos ] + ndays[ pos ] + overlap
      pos = pos + 1
    }
    rv = c(rv, rep( group_id, pos - start_group  ))
    group_id = group_id + 1
  }
  rv
}


```

 1) find contiguious and/or overlapping multi drug episodes
 2) find the doctor consults within that period
 3) create df_intersect, containing every intersection of the entire multi script episode with any doctor consults

```{r}




if (file.exists( intersect_filename )) {
  load( intersect_filename, verbose=TRUE )
} else {
  #


  df_pbs %>%
    mutate( row_id = row_number() ) %>%
    group_by( pin ) %>%
    arrange( pin, spply_dt ) %>%
    mutate( group = find_multi_script_group( spply_dt, quantity)) %>%
    group_by( pin, group ) %>%
    arrange( pin, spply_dt, group ) %>% 
    mutate( gl = max( spply_dt ) - min(spply_dt ), 
           ndays = sum(quantity ),
           nscripts = n()) %>%
    filter( nscripts > 1 ) %>% 
    { . } -> df_pbs_multi_groups
  #
  #
  df_pbs_multi_groups  %>%
    group_by( pin, group, nscripts ) %>%
    summarise( start_date = min( spply_dt ) - 7, 
              end_date = max( spply_dt ),
              quantity = sum(quantity)
              ) %>%
    group_by( pin ) %>%
    select( pin,  start_date, end_date, group, quantity, nscripts) %>% 
    nest( start_date, end_date,  group, quantity, nscripts, .key=pbs ) %>%
    { . } -> df_pbs_nested
  #
  #
  df_mbs %>%
    group_by(pin) %>%
    mutate( end_date = spply_dt + 7,
           start_date = spply_dt - 7) %>%
     select( pin, spr, spply_dt, start_date, end_date) %>% 
    nest( spr, spply_dt, start_date, end_date, .key=mbs ) %>%
    { . } -> df_mbs_nested
  #
  #
  no_cores <- detectCores() - 1
  cluster <- create_cluster(no_cores)
  #
  df_mbs_nested %>%
    inner_join( df_pbs_nested ) %>% 
    partition(pin, cluster=cluster )  %>%
    { . } -> df_both
  #
  cluster_library(df_both, c("tidyverse", "IRanges", "fuzzyjoin"))
  #
  #
  df_both %>%
    do( joined = interval_inner_join( data.frame(.$mbs), 
                                     data.frame(.$pbs), 
                                     by=c('start_date','end_date') ))  %>%
  collect() %>%
  ungroup() %>%
  unnest() %>% 
  { . } -> df_intersect
  #
  #
  #
  save(df_intersect, file=intersect_filename)

}

```

# analysis - number of distinct practicioners for each period
Greater than 2 distinct practicioners, less than 10 days per practicioner, greater than 1 scripts

```{r analysis1}

df_intersect %>%
  mutate( ndays = end_date.y - start_date.y ) %>%
  filter( ndays < 2000 ) %>%
  group_by( pin, group, ndays, nscripts ) %>%
  distinct( spr ) %>%
  count( sort=TRUE) %>%
  rename( distinct_spr_n = n ) %>%
  mutate( days_per_spr = ndays / distinct_spr_n) %>%
  arrange( days_per_spr) %>%
  filter( distinct_spr_n > 1 & days_per_spr < 10  & nscripts > 2 ) %>%
  group_by( pin ) %>% 
  count() %>% 
  { . } -> df_doctor_shoppers


df_doctor_shoppers %>%
  inner_join( df_people ) %>% 
  { . } -> df_doctor_shoppers

df_intersect %>%
  mutate( ndays = end_date.y - start_date.y ) %>%
  filter( ndays < 2000 ) %>%
  group_by( pin, group, ndays  ) %>%
  summarise( quantity = sum( quantity)) %>%
  mutate( pills_per_day = quantity / as.integer( ndays) )


df_doctor_shoppers %>%
  ggplot( aes( sex, fill=sex )) +
  geom_bar()

df_doctor_shoppers %>%
  ggplot( aes(age_group, fill=sex )) +
  geom_bar()

df_doctor_shoppers %>%
  ggplot( aes(age_group, fill=sex )) +
  geom_bar( position='dodge') 


df_doctor_shoppers %>%
  ggplot( aes( sex, age, fill=sex )) +
  geom_boxplot()

df_doctor_shoppers %>%
  ggplot( aes( sex, age, fill=sex )) +
  geom_violin()


df_pbs %>%
  inner_join( df_people ) %>%
  left_join( df_doctor_shoppers, by='pin') %>%
  mutate( type = ifelse( is.na(n ), 'use', 'misuse') ) %>% 
  rename( sex = sex.x, age = age.x, age_group = age_group.x ) %>%
  { . } -> df_combined


df_combined  %>%
  filter( type=='misuse' ) %>%
  group_by( pin, sex, age, type ) %>%
  summarise( quantity = sum( quantity )) %>%
  ggplot( aes( sex, quantity, fill=sex )) + 
  geom_violin() 

df_combined  %>%
  filter( type=='misuse' ) %>%
  group_by( pin, sex, age, type ) %>%
  summarise( quantity = sum( quantity )) %>%
  ggplot( aes( sex, quantity, fill=sex )) + 
  geom_boxplot() +
  scale_y_log10() + ggtitle ('average pills per person, log scale')

```

average number of pills / script

```{r}

df_combined  %>%
  filter( type=='misuse' ) %>%
  group_by( sex ) %>%
  summarise( quantity = sum( quantity ) / n())


df_doctor_shoppers  %>%
  ggplot( aes( age_group, fill=sex  )) + 
  geom_histogram(stat='count', position='dodge' ) 





```
